---
output:
  github_document:
    html_preview: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, knitr_setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = TRUE,
  out.width='750px', dpi=200,
  comment = "#>",
  fig.path = "README-"

)
```

# tpca
An `R` package for automatically selecting which principal components
to keep for detecting changes in the mean and/or covariance matrix.
The choice of principal axes to project data onto is *tailored* to a normal 
state covariance matrix and a customizable distribution over relevant 
change scenarios. Functionality for both regular PCA and dynamic PCA exists.

## Overview
Functionality:

* A function for tailoring PCA to a regular covariance matrix.
* A function for tailoring PCA to a covariance matrix based on lagged observations, i.e., a dynamic PCA variant.
* A generic function for setting up a uniform change distribution.
* Functions for generating random correlation matrices, covariance matrices and
  correlation matrix estimates.
* Summary and plot functions.

TPCA is designed to be used in for instance high-dimensional sensor network applications,
where changes in the mean and/or covariance matrix indicates a system fault.
TPCA helps reduce the dimension to those principal components that are most
sensitive to the relevant changes. This both saves computation and can
increase the precision or speed with which changes are detected.

## Installation
From inside `R`, use the following command:
```{r install, eval = FALSE}
# install.packages("devtools")
devtools::install_github("Tveten/tpca")
# library(tpca)
```

## Usage
```{r example, echo = TRUE}
library(tpca)
cor_mat <- rcor_mat(10)  # Generate random correlation matrix.
tpca_obj <- tpca(cor_mat, change_distr = 'semisparse_uniform', cutoff = 0.99)
ggplot_types(tpca_obj)
ggplot_sparsities(tpca_obj)
ggplot_prop(tpca_obj)
summary(tpca_obj)
```

## Description

## References
