---
output:
  github_document:
    html_preview: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, knitr_setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = TRUE,
  out.width='750px', dpi=200,
  comment = "#>"
)
```

# tpca
An `R` package for automatically selecting which principal components
to keep for detecting changes in the mean and/or covariance matrix.
The choice of principal axes to project data onto is *tailored* to a normal 
state covariance matrix and a customizable distribution over relevant 
change scenarios. Functionality for both regular PCA and dynamic PCA exists.

## Overview
Functionality:
* A function for tailoring PCA to a regular covariance matrix.
* A function for tailoring PCA to a covariance matrix based on lagged observations.
* A generic function for setting up a uniform change distribution.
* Functions for generating random correlation matrices, covariance matrices and
  correlation matrix estimates.
* Plot functions.

TPCA is designed to be used in for instance sensor network applications,
where changes in the mean and/or covariance matrix indicates a system fault.
TPCA helps reduce the dimension to those principal components that are most
sensitive to the relevant changes.

## Installation
From inside `R`, use the following command:
```{r install, eval = FALSE}
# install.packages("devtools")
devtools::install_github("Tveten/tpca")
# library(tpca)
```

## Description

## Usage
See the documentation of the tpca-function.

## References
